### 2022-10-18 chapters/conclusion.tex
Proofreading

\paragraph{raising awareness of the energy consumption of the Softwares}
While this thesis's main focus was to optimize energy consumption using comparative studies, it was easier to say that approach \texttt{X} is greener than approach \texttt{Y}, no matter which metric we were using.
However, it will not be the case for developers when measuring the energy consumption of their programs.
Some tried to give labels, such as (A,B,C\dots), while others translated these raw metrics in an equivalent of fuel consumption (e.g., 1 liter of fuel per 1000 lines of code).
Most of the approaches were to use the carbon emission, such as~\cite{patterson2021carbon} or ecograder~\link{https://ecograder.com/} as a pivot metrics to quantify the environmental cost of osftware.
We intend to explore these approaches and study how they can be used to increase awareness of the energy consumption of their code.

\subsection*{Representativeness}:
As reported in the state of the art, a successful benchmark meets three criteria: reproducibility, accuracy, and representativeness.
This Ph.D. thesis mostly discussed two of these criteria: reproducibility, and accuracy.
However, we did not discuss the representativeness of our benchmarks.
We relied on state-of-the-art benchmarks to represent real-world applications.
Nevertheless, the gap between these benchmarks and the industry is getting bigger and bigger, due to the extreme pace of software development.
In the future, we would like to tackle the issue of representativeness and discuss how we can improve our protocol to fit real-world applications.
After all, what is the purpose of doing optimizations if they cannot be applied to real-world applications?

>>>>

\paragraph{Raising awareness about the energy consumption of software}
As the core focus of this PhD thesis was to optimize energy consumption using comparative studies, it was straightforward to claim that approach \texttt{X} is greener than \texttt{Y}, no matter the metrics we were using.
However, this cannot be the case for developers when measuring the energy consumption of their programs.
Some tried to give labels, such as (A,B,C\dots), while others translated these raw metrics in an equivalent of fuel consumption (e.g., 1 liter of fuel per $1,000$ lines of code).
Most of the approaches were to use the carbon emission, such as~\cite{patterson2021carbon} or ecograder,\link{https://ecograder.com/} as a pivot metrics to quantify the environmental cost of software.
We intend to explore these approaches and study how they can be used to increase awareness of the energy consumption of their code.

\subsection*{Representativeness}
As reported in the state of the art, a successful benchmark meets three criteria: reproducibility, accuracy, and representativeness.
This Ph.D. thesis mostly discussed two of these criteria: reproducibility, and accuracy.
However, we did not discuss the representativeness of our benchmarks.
We relied on state-of-the-art benchmarks to represent real-world applications.
Nevertheless, the gap between these benchmarks and the industry is getting bigger and bigger, due to the extreme pace of software development.
In the future, we would like to tackle the issue of representativeness and discuss how we can improve our protocol to fit real-world applications.
After all, what is the purpose of doing optimizations if they cannot be applied to real-world applications?
